---
title: 'Whisker: Sections with Non-Empty Lists'
author: "Christopher Brown"
date: "March 31, 2016"
output: html_document
---

While *whisker* supports sections, it  does not appear to support sections with non-empty lists as described in <https://mustache.github.io/mustache.5.html>:

Template:

    {{#repo}}
      <b>{{name}}</b>
    {{/repo}}
    
Hash:

    {
      "repo": [
        { "name": "resque" },
        { "name": "hub" },
        { "name": "rip" }
      ]
    }
    
Output:

    <b>resque</b>
    <b>hub</b>
    <b>rip</b>


## Using JSON

This closely follows the mustache documentation by using`jsonlite` to convert the hash to an R object. The R object is a list with a data frame of 3 rows.

```{r}
library(jsonlite)
library(whisker)

tmpl <- 
  "{{#repo}}
  <b>{{name}}</b>
  {{/name}}"

hash <- 
  '{
    "repo": [
      { "name": "resque" },
      { "name": "hub" },
      { "name": "rip" }
    ]
  }'

data <- fromJSON(hash)  # list of data.frame not list of list


whisker_render(tmpl,data)   
```

This does not conform to the specification is not correct as in collapses the `name` column rather than returning three results. According to the specification, I would expect this result:

```{r}
c("<b>resque</b>","<b>hub</b>","<b>rip</b>")
```


## Using list-of-lists 

Using a list of lists does not work either:

```{r}
data <- list( repo = list( name="resque", name="hub", name="rip") )
whisker_render(tmpl,data) 
# [1] "<b>resque</b>"

```



